\TheTitle

### 2017-06-29 paper/methodology.tex
Methodlogy: Fixing sentence
sentence didn't make sense, but now it does

As understanding where the merge begins and ends, the merge task set
will always be the first task set presented; however, the questions will
still be re-ordered within the task set.

>>>>

As understanding where the merge begins and ends is vital to answering
the other question, the merge task set will always be the first task set
presented; however, the questions will still be re-ordered within the
task set.
